\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-26 manuscript/main.tex
new file:   .vscode/settings.json 	deleted:    analysis/counting_number_of_stores.cpp 	deleted:    analysis/network_estimation.ipynb 	modified:   manuscript/main.aux 	modified:   manuscript/main.blg 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   network_estimation/network_estimation.ipynb 	new file:   network_estimation/network_formulation.cpp 	new file:   network_estimation/network_fo

>>>>

\section{Collaborative Spillover Effect} \label{sec:network_effect}

The last section is to estimate the Lianjia's collaborative spillover effect. Lianjia decided to change from brokerage's direction operation to a combination of platform. By attracting other brokerage's into the network will initially make the brokreage's profit down because attracting other people in the platform meaning the market share would be decreased due to the intense competition. However, after the setup of the platform, the market will be more productive and more competitive to occupying a larger share of the whole network. This mechanism is more likely to get better control over the listing and people are more willing to list their house on this platform. Then accordin to the this would be resulted in a winners-take-all market.

In this case, we need to empirically estimate the spillover effect, and if this spillover effect is significant in this setting then people's reaction

To set up, we first match the brokerages' with the
